### 2023-07-17 paper/sec-dis-pseudodata.tex
Update sec-dis-pseudodata.tex

 Fig.~\ref{fig:fasernu2_muon} displays the
 event yields per bin,  Eq.~(\ref{eq:event_yields}),
  for muon neutrinos detected at FASER$\nu$2 restricted
  to the DIS region defined by Eq.~(\ref{eq:DISconditions}).
  %
  We present results binned in $x$ and $Q^2$ and integrated over all available neutrino energies.
  %
  The red dot indicates the weighted center of each bin.
  %
  Adding up all bin entries results into the $N_{\nu_\mu}$ value
  for reconstructed muon
  neutrinos listed in
  Table~\ref{tab:integrated_rates}.
  %
  Only bins with at least 30 events are retained, to ensure the validity of Gaussian
  statistics.
  %
  One observes large event rates for most of the region in $\lp x,Q^2\rp$ covered,
  leading to typical statistical uncertainties at the 1\% level or smaller.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[t]
    \centering
    \includegraphics[width = 0.9\textwidth]{plots/Kin_nNNPDF30_EIC_FPF.pdf}
    \caption{The kinematic coverage of FASER$\nu$2 in the $(x,Q^2)$ plane,
      same as  Fig.~\ref{fig:fasernu2_muon},
      compared to that of electron-ion collisions
      at the EIC for the highest center-of-mass energies $\sqrt{s}$ planned,
      as well as to the coverage of other available hard-scattering datasets involving
      nuclear targets or projectiles.
      %
      Specifically, we display the coverage of fixed-target neutral- and charged-current nuclear DIS,
      fixed-target Drell-Yan production, and $W$, $Z$, $D$-meson, photon, and dijet
      production in proton-lead collisions at the LHC.
      }
    \label{fig:Kin_nNNPDF30_EIC_FPF}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

 Fig.~\ref{fig:fasernu2_muon} displays the
 event yields per bin,  Eq.~(\ref{eq:event_yields}),
 for muon neutrinos detected at the
 FASER$\nu$, SND@LHC, FASER$\nu$2, and FLArE  experiments,
 restricted
 to the DIS region defined by Eq.~(\ref{eq:DISconditions})
 and where only bins with $\ge 30$ events are retained.
 %
 Adding up the bins in each of the panels results into the numbers listed in
 Table~\ref{tab:integrated_rates}.
 %
 The clear improvement in going frm FASER$\nu$, SND@LHC
 to the FPF experiments related not only to the number
 of events but also to the kinematic coverage,
 %
 For the FPF experiments,m 
 One observes large event rates for most of the region in $\lp x,Q^2\rp$ covered,
 leading to typical statistical uncertainties at the 1\% level or smaller,
 while for FASER$\nu$, SND@LHC statistical uncertainties are much larger.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[t]
    \centering
    \includegraphics[width = 0.9\textwidth]{plots/Kin_nNNPDF30_EIC_FPF.pdf}
    \caption{The kinematic coverage in the $(x,Q^2)$ plane
      of muon neutrino scattering
      at FASER$\nu$2, FLArE,
      and AdvSND (see also Fig.~\ref{fig:fasernu2_muon})
      compared to that of electron-ion collisions
      at the EIC for the highest center-of-mass energies $\sqrt{s}$ planned,
      as well as to the coverage of other available hard-scattering datasets involving
      nuclear targets or projectiles.
      %
      Specifically, we display the coverage of fixed-target neutral- and charged-current nuclear DIS,
      fixed-target Drell-Yan production, and $W$, $Z$, $D$-meson, photon, and dijet
      production in proton-lead collisions at the LHC.
      }
    \label{fig:Kin_nNNPDF30_EIC_FPF}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
